### 2014-09-17 ms/ms.Rmd
Add author affiliations. Closes #159

```{r,results="asis",echo=FALSE, message=FALSE}
writeLines(paste("**List of Authors:**", pasteC(listOfAuthors(baad$contact), ', ')))
```

>>>>

```{r,results="asis",echo=FALSE, message=FALSE}
details <- authorDetails(baad$contact)

writeLines(paste("**List of Authors:** ", paste0(details$authors, "^", details$address_code,"^",collapse = ", ") ))

writeLines("\n\n")

writeLines(paste0(details$address$code, ". ", details$address$address, collapse="\n"))
```
